Mechanization of Separation in Generic Extensions

### 2019-01-05 LICS/isabelle.tex
Referencias a papers sobre Isabelle. Cambio en la explicación de Isar.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%          
\section{Isabelle}
\label{sec:isabelle}
%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-
\subsection{Logics}
\label{sec:logics}
Isabelle provides a meta-language called \emph{Pure} that consists of
a fragment of higher order logic, where \isatt{\isasymRightarrow} is
the function-space arrow. The meta-Boolean type is called
\isatt{prop}. Meta-connectives
\isatt{\isasymLongrightarrow} and \isatt{\&\&\&} fulfill the role of
implication and conjunction, and the meta-binder \isatt{\isasymAnd}
corresponds to universal quantification.

@@

The source code is written for the 2018 version of Isabelle (with
minor modifications, it can be run in Isabelle2016-1). Most of it is
presented in the (nowadays standard) declarative flavour called
\emph{Isar} \cite{DBLP:conf/tphol/Wenzel99}, where intermediate
statements in the course 
of a proof are explicitly stated, interspersed with automatic 
tactics handling more trivial steps. The goal is that the resulting
text, a \emph{proof document}, can be understood without the need of
running it.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%          
\section{Isabelle}
\label{sec:isabelle}
%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-
\subsection{Logics}
\label{sec:logics}
Isabelle \cite{Isabelle,DBLP:books/sp/Paulson94} provides a
meta-language called \emph{Pure} that consists of a fragment of higher
order logic, where \isatt{\isasymRightarrow} is the function-space
arrow. The meta-Boolean type is called \isatt{prop}. Meta-connectives
\isatt{\isasymLongrightarrow} and \isatt{\&\&\&} fulfill the role of
implication and conjunction, and the meta-binder \isatt{\isasymAnd}
corresponds to universal quantification.

@@

The source code is written for the 2018 version of Isabelle (with
minor modifications, it can be run in Isabelle2016-1). Most of it is
presented in the (nowadays standard) declarative flavour called
\emph{Isar} \cite{DBLP:conf/tphol/Wenzel99}, where intermediate
statements in the course of a proof are explicitly stated,
interspersed with automatic tactics handling more trivial steps. The
goal is that the resulting text, a \emph{proof document}, can be
understood without the need of re-playing it viewing the proof state
at each point.
